---
title: "Predicting the Default of Credit Card Clients"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{=html}
<style>
  h1, h2, h3, h4, h5, h6 {
   font-family: et-book, Palatino, "Palatino Linotype", "Palatino LT STD", "Book Antiqua", Georgia, serif;
  }
  body {
  background-color: #fffff8;
}
</style>
```

<hr style="border: 2px solid black;">

```{r include=FALSE}
library(readr) # Package for loading the csv file. 
library(dplyr) # Package for manipulate DATA .
library(ggplot2) # Package for visualize DATA .
library(plotly) # Package for visualizing DATA in a interactive way .
library(corrplot)  # Package for visualizing correlation matrices .
library(DescTools) # Package for descriptive statistics and visualization tools .
library(ltm)
library(vcd)
library(knitr)
library(kableExtra)
library(infotheo)
library(caret)
library(caTools)
library(randomForest)
library(scorecard)
library(officer)

path_data <- "D:\\project_PFA Default of Credit Card Clients_Dataset_SAMER\\Initial_Dataset\\UCI_Credit_Card.csv"
UCI_Credit_Card <- data.frame(read.csv(path_data))


UCI_Credit_Card<-subset(UCI_Credit_Card,select = -ID) 

colnames(UCI_Credit_Card)[colnames(UCI_Credit_Card) == "PAY_0"] <- "PAY_1"
colnames(UCI_Credit_Card)[colnames(UCI_Credit_Card) == "default.payment.next.month"] <- "Payment_Status"

col_names_Quanti<-c("LIMIT_BAL","AGE",
                      "BILL_AMT1","BILL_AMT2","BILL_AMT3","BILL_AMT4","BILL_AMT5","BILL_AMT6",
                      "PAY_AMT1","PAY_AMT2","PAY_AMT3","PAY_AMT4","PAY_AMT5","PAY_AMT6")
col_names_Cato<-c("SEX","EDUCATION","MARRIAGE",
                     "PAY_1","PAY_2","PAY_3","PAY_4","PAY_5","PAY_6",
                     "Payment_Status")
all_col_names<-c(col_names_Quanti,col_names_Cato)

for (nc in col_names_Cato) {
  UCI_Credit_Card[[nc]]<-as.factor(UCI_Credit_Card[[nc]])      
}
```

## Univariate Analysis:

### Qantitative DATA

```{r}
summary(UCI_Credit_Card[col_names_Quanti])
```

> We have:<br> - Negative BILL_AMT ? We should investigate that .<br>

### Analysing LIMIT_BAL using histogram

```{r}
gg <- ggplot(UCI_Credit_Card, aes(x = LIMIT_BAL, fill = Payment_Status)) +
  geom_histogram( color = "black") +
  labs(title = "Distribution of LIMIT_BAL by Payment_Status",
       x = "LIMIT_BAL",
       y = "Count",
       fill = "Payment_Status") +
  theme_minimal()#+
  #theme(plot.background = element_rect(fill = "#fffff8"))


ggplotly(gg)
```

> 50k is the most frequent LIMIT_BAL

### Checking LIMIT_BAL Distribution unsing Q-Q plot

```{r}
ggplot(data = UCI_Credit_Card, aes(sample = LIMIT_BAL)) +
  stat_qq() +
  stat_qq_line(col = "red") +
  labs(title = "Q-Q Plot for LIMIT_BAL")


```

> Asymmetrical Distribution (positively skewed)

### Analysing AGE using histogram

```{r}
gg <- ggplot(UCI_Credit_Card, aes(x = AGE, fill = Payment_Status)) +
  geom_histogram( color = "black") +
  labs(title = "Distribution of AGE by Payment_Status",
       x = "AGE",
       y = "Count",
       fill = "Payment_Status") +
  theme_minimal()#+
  #theme(plot.background = element_rect(fill = "#fffff8"))


ggplotly(gg)
```

> The most frequent AGE is 29.

### Checking AGEL Distribution unsing Q-Q plot

```{r}
ggplot(data = UCI_Credit_Card, aes(sample = AGE)) +
  stat_qq() +
  stat_qq_line(col = "red") +
  labs(title = "Q-Q Plot for AGE")
```

> Asymmetrical Distribution (positively skewed).

### Analysing BILL_AMT(i) using histogram

```{r}

BILL_AMT_LIST<-list("BILL_AMT1","BILL_AMT2","BILL_AMT3","BILL_AMT4","BILL_AMT5","BILL_AMT6")
histogram_list <- lapply(BILL_AMT_LIST, function(col_name) {
    plot_ly(UCI_Credit_Card, x = ~get(col_name), type = "histogram", histnorm = "probability density",nbinsx = 80,name = col_name) %>%
      layout(title = "Histograms of Bill Amounts")
  })
  combined_plot <- subplot(histogram_list, nrows = 3)
  combined_plot
```

> We can't see much from those plots

### Using Q_Q plot to check the distrubution

#### 1.BILL_AMT1

```{r}
ggplot(data = UCI_Credit_Card, aes(sample = BILL_AMT1)) +
  stat_qq() +
  stat_qq_line(col = "red") +
  labs(title = "Q-Q Plot for BILL_AMT1")

```

#### 2.BILL_AMT2

```{r}
ggplot(data = UCI_Credit_Card, aes(sample = BILL_AMT2)) +
  stat_qq() +
  stat_qq_line(col = "red") +
  labs(title = "Q-Q Plot for BILL_AMT2")

```

#### 3.BILL_AMT3

```{r}
ggplot(data = UCI_Credit_Card, aes(sample = BILL_AMT3)) +
  stat_qq() +
  stat_qq_line(col = "red") +
  labs(title = "Q-Q Plot for BILL_AMT3")

```

#### 4.BILL_AMT4

```{r}
ggplot(data = UCI_Credit_Card, aes(sample = BILL_AMT4)) +
  stat_qq() +
  stat_qq_line(col = "red") +
  labs(title = "Q-Q Plot for BILL_AMT4")

```

#### 5.BILL_AMT5

```{r}
ggplot(data = UCI_Credit_Card, aes(sample = BILL_AMT5)) +
  stat_qq() +
  stat_qq_line(col = "red") +
  labs(title = "Q-Q Plot for BILL_AMT5")

```

#### 6.BILL_AMT6

```{r}
ggplot(data = UCI_Credit_Card, aes(sample = BILL_AMT6)) +
  stat_qq() +
  stat_qq_line(col = "red") +
  labs(title = "Q-Q Plot for BILL_AMT6")

```

> The distribution of variables can influence both the correlation between variables and the choice of model used for analysis.

BILL_AMT(i) :Amount of bill statement in month (i), 2005 (NT dollar) .So ,what does negative value mean

```{r}
negative_BILL_AMT<-UCI_Credit_Card %>%
  filter(BILL_AMT1 < 0 | BILL_AMT2 < 0 | BILL_AMT3 < 0 | BILL_AMT4 < 0 | BILL_AMT5 < 0 | BILL_AMT6 < 0)
head(negative_BILL_AMT)
```

> Hypothesis: It may imply that the bank owes them money, as they are making payments exceeding what is expected.

### Using histogram visualisation for "PAY_AMT(i)"

```{r}
PAY_AMT_list<-c("PAY_AMT1","PAY_AMT2","PAY_AMT3","PAY_AMT4","PAY_AMT5","PAY_AMT6")

histogram_list <- lapply(PAY_AMT_list, function(col_name) {
    plot_ly(UCI_Credit_Card, x = ~get(col_name), type = "histogram",nbinsx = 70 ,name = col_name) %>%
      layout(title ="Histograms of Pay Amounts")
  })
  combined_plot <- subplot(histogram_list, nrows = 3)
  combined_plot
```

> The distribution of PAY_AMT is heavily skewed and violates the assumption of normality. \> We can consider applying a log transformation to the data to make the distribution more symmetric.

```{r}
# Define a small constant to add to the variable
epsilon <- 1e-10


histogram_list <- lapply(PAY_AMT_list, function(col_name) {
    plot_ly(UCI_Credit_Card, x = ~log(get(col_name) + epsilon), type = "histogram", nbinsx = 70 , name = col_name) %>%
      layout(title = "Histograms of Pay Amounts")
})


combined_plot <- subplot(histogram_list, nrows = 3)
combined_plot
```

### Catagorical DATA

```{r}
summary(UCI_Credit_Card[col_names_Cato])
```

### Using Pie Chart for SEX

```{r message=FALSE, warning=FALSE}

SEX_counts <- table(UCI_Credit_Card$SEX)

plot_ly(labels = c("Male", "Female"), values = SEX_counts, type = 'pie') %>%
  layout(annotations = list(
      x = 0,
      y = 1,
      xref = "paper",
      yref = "paper",
      text = "Pie Chart for SEX",
      font = list(color = "black", size = 20),
      showarrow = FALSE),piecolorway = c( "pink","blue"))



```

> We have more than half female

### Using Pie Chart for EDUCATION

```{r message=FALSE, warning=FALSE}
EDUCATION_counts <- table(UCI_Credit_Card$EDUCATION)
EDUCATION_counts
plot_ly(labels = list("unlabel","graduate school","university", "high school", "others", "unknown", "unknown"), values = EDUCATION_counts, type = 'pie') %>%
  layout(annotations = list(
      x = 0,
      y = 1,
      xref = "paper",
      yref = "paper",
      text = "Pie Chart for EDUCATION",
      font = list(color = "black", size = 15),
      showarrow = FALSE))

```

### Using Pie Chart for MARRIAGE

```{r message=FALSE, warning=FALSE}
MARRIAGE_counts <- table(UCI_Credit_Card$MARRIAGE)
MARRIAGE_counts
plot_ly(labels = c("unlabel","married", "single", "others"), values = MARRIAGE_counts, type = 'pie') %>%
  layout(annotations = list(
      x = 0,
      y = 1,
      xref = "paper",
      yref = "paper",
      text = "Pie Chart for MARRIAGE",
      font = list(color = "black", size = 15),
      showarrow = FALSE))

```

### Using barplot for "PAY_0"

```{r message=FALSE, warning=FALSE}
labels_PAY <- c("-2" = "unlabel(-2)", "-1" = "pay duly", "0" = "unlabel(0)",
                  "1" = "pay_del_1_mth", "2" = "pay_del_2_mths",
                  "3" = "pay_del_3_mths", "4" = "pay_del_4_mths",
                  "5" = "pay_del_5_mths", "6" = "pay_del_6_mths",
                  "7" = "pay_del_7_mths", "8" = "pay_del_8_mths",
                  "9" = "pay_del_9_mths_above")
ggplotly(
ggplot(UCI_Credit_Card, aes(x = PAY_1, fill = PAY_1)) +
  geom_bar() +
  labs(title = "Bar Plot by PAY_1", y = "Frequency") +
  theme_classic() +
  scale_x_discrete(labels = labels_PAY)+theme(axis.text.x = element_text(angle = 45, hjust = 1))
)

```

> unlabel(0) is the most frequent category

### Using barplot for "PAY_2"

```{r message=FALSE, warning=FALSE}
ggplotly(
ggplot(UCI_Credit_Card, aes(x = PAY_2, fill = PAY_2)) +
  geom_bar() +
  labs(title = "Bar Plot by PAY_2", y = "Frequency") +
  theme_classic() +
  scale_x_discrete(labels = labels_PAY)+theme(axis.text.x = element_text(angle = 45, hjust = 1))
)
```

> unlabel(0) is the most frequent category

### Using barplot for "PAY_3"

```{r message=FALSE, warning=FALSE}
ggplotly(
ggplot(UCI_Credit_Card, aes(x = PAY_3, fill = PAY_3)) +
  geom_bar() +
  labs(title = "Bar Plot by PAY_3", y = "Frequency") +
  theme_classic() +
  scale_x_discrete(labels = labels_PAY)+theme(axis.text.x = element_text(angle = 45, hjust = 1))
)
```

> unlabel(0) is the most frequent category

### Using barplot for "PAY_4"

```{r message=FALSE, warning=FALSE}
ggplotly(
ggplot(UCI_Credit_Card, aes(x = PAY_4, fill = PAY_4)) +
  geom_bar() +
  labs(title = "Bar Plot by PAY_4", y = "Frequency") +
  theme_classic() +
  scale_x_discrete(labels = labels_PAY)+theme(axis.text.x = element_text(angle = 45, hjust = 1)
))
```

> unlabel(0) is the most frequent category

### Using barplot for "PAY_5"

```{r message=FALSE, warning=FALSE}
ggplotly(
ggplot(UCI_Credit_Card, aes(x = PAY_5, fill = PAY_5)) +
  geom_bar() +
  labs(title = "Bar Plot by PAY_5", y = "Frequency") +
  theme_classic() +
  scale_x_discrete(labels = labels_PAY)+theme(axis.text.x = element_text(angle = 45, hjust = 1))
)

```

> unlabel(0) is the most frequent category

### Using barplot for "PAY_6"

```{r message=FALSE, warning=FALSE}
ggplotly(
ggplot(UCI_Credit_Card, aes(x = PAY_6, fill = PAY_6)) +
  geom_bar() +
  labs(title = "Bar Plot by PAY_6", y = "Frequency") +
  theme_classic() +
  scale_x_discrete(labels = labels_PAY)+theme(axis.text.x = element_text(angle = 45, hjust = 1))
)

```

> unlabel(0) is the most frequent category

> > we should investigate unlabel(0)

### Using Charpie for Payment_Status :

```{r message=FALSE, warning=FALSE}
PayStatue_counts <- table(UCI_Credit_Card$Payment_Status)

plot_ly(labels = c("Non_default", "Default"), values = PayStatue_counts, type = 'pie') %>%
  layout(annotations = list(
      x = 0,
      y = 1,
      xref = "paper",
      yref = "paper",
      text = "Pie Chart for\n Payment_Status",
      font = list(color = "black", size = 14),
      showarrow = FALSE),piecolorway = c("blue", "lightcoral"))


```

> Nearly 80 % did not default
