---
title: "Predicting the Default of Credit Card"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
---
Prediction of Credit Card Default
```{=html}
<style>
  h1, h2, h3, h4, h5, h6 {
   font-family: et-book, Palatino, "Palatino Linotype", "Palatino LT STD", "Book Antiqua", Georgia, serif;
  }
  body {
  background-color: #fffff8;
}
</style>
```
<hr style="border: 2px solid black;">

## Project Overview

-   **Author:** Dridi Slim\
    **Date:** February 11, 2024\
    **Institution:** [ESSAI](http://www.essai.rnu.tn/)\
    **Supervisor:** [Professor Samer Azzabi](https://www.linkedin.com/in/samer-azzabi-5449691b3/)

<hr style="border: 2px solid black;">

### Project Goal

The primary objective of this project is to develop a predictive model for determining the likelihood of credit card clients defaulting on their payments.

<hr style="border: 2px solid black;">

## Checking the data

### Load Libraries

```{r,message=FALSE, warning=FALSE}
library(readr) # Package for loading the csv file. 
library(dplyr) # Package for manipulate DATA .
library(ggplot2) # Package for visualize DATA .
library(plotly) # Package for visualizing DATA in a interactive way .
library(corrplot)  # Package for visualizing correlation matrices .
library(DescTools) # Package for descriptive statistics and visualization tools .
library(ltm)
library(vcd)
library(knitr)
library(kableExtra)
library(infotheo)
library(caret)
library(caTools)
library(randomForest)
library(scorecard)
library(officer)
```

------------------------------------------------------------------------

### Load Data

```{r}
path_data <- "D:\\project_PFA Default of Credit Card Clients_Dataset_SAMER\\Initial_Dataset\\UCI_Credit_Card.csv"
UCI_Credit_Card <- data.frame(read.csv(path_data))


```

------------------------------------------------------------------------

### Overview of the Data

```{r warning=FALSE}
head(UCI_Credit_Card)
```

### Check the info of our DATA

```{r}
describe(UCI_Credit_Card)
```

> We have : <br> - Categorical DATA set to int type we should pay attention to that.<br> - A gap between PAY_0 and PAY_2 we should investigate why.<br> - ID column is useless we should do something about it.<br> - Our target variable is default.payment.next.month.<br>

### Check is their any NA

```{r}
colSums(is.na(UCI_Credit_Card)) #calculating in every col the NA value
```

> We have no Missing DATA

<hr style="border: 1px solid black;">

[Next Page]("Analyse.html")

